Appendix: New and simplified manual controls for projection and slice tours

### 2022-09-30 paper/appendix.Rmd
figure link made

The slice center, $c$, from Equation 1 in the main paper, is a point in the $p$-dimensional space. By default it is placed in the center of the data (plot A). Moving this along a variable axis moves the slice outwards from the center of the data (plots B, C).

>>>>

The slice center, $c$, from Equation 1 in the main paper, is a point in the $p$-dimensional space. By default it is placed in the center of the data (Figure \ref{fig:anchornav} A). Moving this along a variable axis moves the slice outwards from the center of the data (Figure \ref{fig:anchornav} B, C).

### 2022-09-30 paper/appendix.tex
figure link made

The slice center, \(c\), from Equation 1 in the main paper, is a point
in the \(p\)-dimensional space. By default it is placed in the center of
the data (plot A). Moving this along a variable axis moves the slice
outwards from the center of the data (plots B, C).

>>>>

The slice center, \(c\), from Equation 1 in the main paper, is a point
in the \(p\)-dimensional space. By default it is placed in the center of
the data (Figure \ref{fig:anchornav} A). Moving this along a variable
axis moves the slice outwards from the center of the data (Figure
\ref{fig:anchornav} B, C).
